\documentclass[a4paper,english,10pt]{article}

\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}
%\usepackage{doublespace}
%\setstretch{1.2}


\definecolor{linkcolour}{rgb}{0, 0.2, 0.6}
\hypersetup{colorlinks, breaklinks, urlcolor=linkcolour, linkcolor=linkcolour}

\usepackage[utf8]{inputenc}

\usepackage{ae}
\usepackage[T1]{fontenc}
\usepackage{CV}
\usepackage[style=british]{csquotes}    % ensures that the proper quotes are used in the bibliography
\usepackage{amssymb}
\usepackage{mathpazo}


\usepackage[
  backend      = biber,
  doi          = false,
  giveninits   = false,
  maxcitenames = 99,
  isbn         = false,
  url          = false,
]{biblatex}
\addbibresource{Publications.bib}

\usepackage[top=0.8in, bottom=0.4in, left=0.5in, right=0.4in]{geometry}


\begin{document}

\pagestyle{empty}

%Ueberschrift
\begin{center}
%\huge{\textsc{Resume}}
%\vspace{\baselineskip}

  \Large{\textsc{Gonzalo Ciruelos}}\\
  \vspace{0.3em}
\footnotesize{
  Address: Rieterstrasse 21 - Z\"urich 8002 - Switzerland $\blacktriangle$ Nationality: Argentine, Spanish \\
  % Phones: +54 114831-9510 / +54 9 1135-722-611
  % Birth Date: 28 February 1995 $\blacktriangle$
  Personal web: \href{http://www.gciruelos.com}{www.gciruelos.com} $\blacktriangle$ Email: gonzalo.ciruelos@gmail.com
}
\end{center}


\section{Professional Experience}
\begin{CV}
\item[Oct 2018--ongoing] Google. Senior Software Engineer.\newline
  \begin{footnotesize}
  \emph{Google Switzerland. Lead of YouTube automated bidding infrastructure. Promoted to SWE III in Oct 2019 and Senior SWE in Oct 2021.}
  \end{footnotesize}
\item[Aug 2016--Sep 2018] University of Buenos Aires. Teaching Assistant.\newline
  \begin{footnotesize}
  \emph{Computer Organization II (Intel x86\_64 architecture and microarchitecture, SIMD processing model, x86 operating system programming and general low-level optimization), and Algorithms and Data Structures III (graph algorithms and computational complexity theory).}
  \end{footnotesize}
\item[Jan 2017--Apr 2017] Google. Software Engineering Intern.\newline
  \begin{footnotesize}
  \emph{Google Los Angeles. I worked on improving performance and adding features to an ad campaign benchmark visualization tool.}
  \end{footnotesize}
\item[Jan 2016--Mar 2016] Google. Software Engineering Intern.\newline
  \begin{footnotesize}
  \emph{Google Waterloo. I worked at the anti-malvertising team.}
  \end{footnotesize}
\end{CV}


\section{Education}
\begin{CV}
\item[2013--2018] Licenciatura en Ciencias de la Computación (Computer Science combined B.Sc. and M.Sc.). University of Buenos Aires. GPA 9.8 (10.0 scale). Thesis: "Factoring Derivation Spaces via Intersection Types", with Pablo Barenbaum
\item[2013--unfinished] Licenciatura en Ciencias Matemáticas (Mathematics combined B.Sc. and M.Sc.). University of Buenos Aires. Completed 3.5 years of a 6.5 years degree. GPA 9.5 (10.0 scale)
% \item[2008--2012] Instituto Libre de Segunda Enseñanza - High School Diploma
\end{CV}


\section{Publications}
\begin{CV}
\item[\href{https://doi.org/10.1007/978-3-030-02768-1_2}{APLAS}] Pablo Barenbaum, Gonzalo Ciruelos. "Factoring Derivation Spaces via Intersection Types". APLAS 2018.
\item[\href{https://doi.org/10.1080/10724117.2018.1524089}{Math Horizons}] Gonzalo Ciruelos. "What is the Roundest Country?".  Math Horizons, 26(3).
\end{CV}


\section{Honors and Awards}
\begin{CV}
% \item [ACM ICPC TAP 2016] Argentine Programming Competition - Ranked 12 out of 63
\item [CIMA 2016] Argentine Intercollegiate Math Competition - 4th place
\item [CIMA 2015] Argentine Intercollegiate Math Competition - 5th place
% \item [ACM ICPC TAP 2014] Argentine Programming Competition - Ranked 18 out of 63
\item [CIMA 2014] Argentine Intercollegiate Math Competition - Honorable Mention
\item [OMA 2011] Argentine Math Olympiad - Made it to IMO selection test
% \item [Other] \hspace{1.5em} Google Code Jam, SPOJ
\end{CV}


\section{Programming Skills}
\begin{CV}
\item[Preferred languages] \hspace{1.2em} C++, Python
\item[Moderate experience] \hspace{0.7em} C, Haskell, Unix shell, HTML/CSS, Javascipt, x86-64 Assembly
\item[Basic experience]  \hspace{2.4em} R, Java
\end{CV}


\section{Other}
\begin{CV}
\item[Github profile] \href{http://www.github.com/gciruelos}{www.github.com/gciruelos}
\item[Languages] Spanish (native), English (fluent), French (elementary), German (elementary)
\item[Interests] Systems programming, Math, Programming languages
\end{CV}

\end{document}
